%-*- coding: utf-8 -*-
%#!pdflatex

%\documentclass[a4paper,10pt]{article}
\documentclass[a4paper,9pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{url}
\newcommand{\etal}{{\it et al.}}
\usepackage{epstopdf}
\usepackage{bm}
\setlength{\oddsidemargin}{-5mm}
\setlength{\evensidemargin}{-5mm}
\setlength{\topmargin}{-20mm}
\setlength{\textwidth}{170mm}
\setlength{\textheight}{260mm}

\title{Hiroshi Kajino}
\date{\today}

%\author{Department of Mathematical Informatics,\\ Graduate School of Information Science and Technology,\\ The University of Tokyo}
\begin{document}
\maketitle
%\vspace{-2cm}
\subsection*{Personal Information}
\begin{itemize}
 \item Degree: PhD of Information Science and Technology
 \item Nationality: Japan
 \item Language: Japanese, English
 \item Affiliation: IBM Research - Tokyo.
 \item Address: 19-21 Hakozaki, Chuo-ku, Tokyo 103-8510, Japan.
 \item E-mail: \url{hiroshi.kajino.1989@gmail.com}
 \item WWW: \url{https://sites.google.com/site/hiroshikajino1989/home}
 \item Github: \url{https://github.com/kanojikajino}
 \item Programming Skills: Python, Java
\end{itemize}
\subsection*{Research Interests}
\begin{itemize}
 \item Machine learning / data mining and their business applications
 \item Molecular optimization
 \item Privacy in machine learning
\end{itemize}

\subsection*{Education}
\begin{itemize}
 \item \textit{PhD of Information Science and Technology}, Apr 2013 -- Mar 2016,\\
Department of Mathematical Informatics, Graduate School of Information Science and Technology, The University of Tokyo, Japan.\\
{\bf Supervisor}: Professor Kenji Yamanishi (co-supervised by Professor Hisashi Kashima).
 \item \textit{Master of Information Science and Technology}, Apr 2011 -- Mar 2013,\\
Department of Mathematical Informatics, Graduate School of Information Science and Technology, The University of Tokyo, Japan.\\
{\bf Title}: Convex Formulations for Learning from Crowds\\
{\bf Supervisor}: Associate Professor Hisashi Kashima.
 \item \textit{Bachelor of Engineering}, Apr 2007 -- Mar 2011, \\
Department of Mathematical Engineering and Information Physics, School of Engineering, The University of Tokyo, Japan.\\
{\bf Title}: Deterministic Random Walks on Finite Graphs [in Japanese]\\
{\bf Supervisor}: Associate Professor Kazuhisa Makino.
\end{itemize}

\subsection*{Work Experience}
\begin{itemize}
 \item Researcher at IBM Research - Tokyo, Apr. 2016-.
 \item Part-time lecturer at Tokyo University of Science, Sep. 2018-.
 \item Part-time lecturer at Doshisha University, Apr. 2022-Sep.2022.
 \item Research internship at IBM Research - Ireland (Supervisor: Akihiro Kishimoto, PhD), Aug.--Oct. 2014.
 \item Research internship at NTT Communication Science Laboratories (Supervisor: Akisato Kimura, PhD), Aug. 2011 \& Nov. 2011.
\end{itemize}

\subsection*{Fellowships}
\begin{itemize}
 \item Microsoft Research Asia Fellowship 2014, Microsoft Research Asia, 2014.
 \item Research Fellowship for Young Scientists (DC2), Japan Society for the Promotion of Science, Apr. 2014--Mar. 2016.
 \item Total Exemption from Repayment of Scholarship Loan for Students with Outstanding Results, Japan Student Services Organization, Mar. 2013.
\end{itemize}

\subsection*{Academic Services}
\begin{itemize}
 \item Reviewers
 \item Mentor for ``Experts on Computer Science'' program (Joho-kagaku-no-tatsujin program)
\end{itemize}


\subsection*{Publications and Talks}

\subsubsection*{Book/Book Chapters}
\begin{itemize}
 \item Hiroshi Kajino: Molecular Optimization Using Machine Learning: From Theory to Practice, Ohm-sha, 2023. [in Japanese]
 \item Masataro Asai, Hiroshi Kajino, Alex Fukunaga, Christian Muise: Symbolic Reasoning in Latent Space: Classical Planning as an Example, Neuro-Symbolic Artificial Intelligence: The State of the Art, Chapter 2, IOS Press, 2022.
\end{itemize}

\subsubsection*{Journal Papers}
\begin{itemize}
 \item Masataro Asai, Hiroshi Kajino, Alex Fukunaga, Christian Muise: Classical Planning in Deep Latent Space, Journal of Artificial Intelligence Research, Vol.74, pp.1599-1686, 2022.
 \item Sho Yokoi, Hiroshi Kajino, Hisashi Kashima. Link Prediction in Sparse Networks Using Incidence Matrix Factorization. Journal of Information Processing, Vol.25, pp.477-485, 2017. 
 \item Shunsuke Kajimura, Yukino Baba, Hiroshi Kajino, Hisashi Kashima: Quality Control for Crowdsourced Enumeration. Journal of Japanese Society of Artificial Intelligence, Vol.31, No.2, pp.xx-xx, 2015. [in Japanese]
 \item Hiroshi Kajino, Hiromi Arai, Hisashi Kashima: Preserving Worker Privacy in Crowdsourcing, Data Mining and Knowledge Discovery, Vol.28, Issue 5, pp.1314-1335, 2014.
 \item Hiroshi Kajino, Yuta Tsuboi, Issei Sato, Hisashi Kashima: Learning from Crowds and Experts, Journal of Japanese Society of Artificial Intelligence, Vol.28, No.3, pp.243-248, 2013. [in Japanese]
 \item Hiroshi Kajino and Hisashi Kashima: Convex Formulations of Learning from Crowds, Journal of Japanese Society of Artificial Intelligence, Vol.27, No.3, pp.133-142, 2012. [in Japanese], {JSAI Best Paper Award}.
\end{itemize}

\subsubsection*{Conference/Workshop Papers (refereed)}
\begin{itemize}
 \item Akihiro Kishimoto, Hiroshi Kajino, Masataka Hirose, Junta Fuchiwaki, Indra Priyadarsini, Lisa Hamada, Hajime Shinohara, Daiju Nakano, Seiji Takeda: MHG-GNN: Combination of Molecular Hypergraph Grammar with Graph Neural Network, NeurIPS 2023 Workshop AI4Mat, 2023.
 \item Hiroshi Kajino, Kohei Miyaguchi, Takayuki Osogami: Biases in Evaluation of Molecular Optimization Methods and Bias Reduction Strategies, ICML-2023, Hawai, 2023.
 \item Hiroshi Kajino: A Differentiable Point Process with Its Application to Spiking Neural Networks, ICML-2021, Virtual, 2021~(short talk).
 \item Hiroshi Kajino: Molecular Hypergraph Grammar with Its Application to Molecular Optimization, ICML-2019, Long Beach, CA, 2019~(long talk).
 \item Masataro Asai, Hiroshi Kajino: Towards Stable Symbol Grounding with Zero-Suppressed State AutoEncoder, ICAPS-2019, Berkeley, CA, 2019.
 \item Kohei Miyaguchi, Hiroshi Kajino: Cogra: Concept-drift-aware Stochastic Gradient Descent for Time-series Forecasting, In Proceedings of the Thirty-Third AAAI Conference on Artificial Intelligence (AAAI-2019), pp.4594-4601, Hawaii, USA, 2019.
 \item Takayuki Osogami, Hiroshi Kajino, Taro Sekiyama: Bidirectional learning for time-series models with hidden units, In Proceedings of the Thirty-fourth International Conference on Machine Learning (ICML-2017), pp.2711-2720, Sydney Australia, 2017.
 \item Hiroshi Kajino: A Functional Dynamic Boltzmann Machine, In Proceedings of the International Joint Conference on Artificial Intelligence 2017 (IJCAI-2017), pp.1987-1993, Melbourne, Australia, 2017.
 \item Sho Yokoi, Hiroshi Kajino, Hisashi Kashima: Link Prediction by Incidence Matrix Factorization, In Proceedings of the 22nd European Conference on Artificial Intelligence (ECAI), The Hague, Holland, 2016.
 \item Shunsuke Kajimura, Yukino Baba, Hiroshi Kajino, Hisashi Kashima: Quality Control for Crowdsourced POI Collection, In Proceedings of the 19th Pacific-Asia Conference on Knowledge Discovery and Data Mining, Ho Chi Minh City, Viet Nam, 2015. Long paper (27/405).
 \item Hiroshi Kajino, Akihiro Kishimoto, Adi Botea, Elizabeth Daly, Spyros Kotoulas: Active Learning for Multi-relational Data Construction, In Proceedings of the 24th International World Wide Web Conference (WWW2015), Florence, Italy, 2015. acceptance rate = 131/929 = 14.1\%.
 \item Hiroshi Kajino, Yukino Baba, Hisashi Kashima: Instance-privacy Preserving Crowdsourcing, In Proceedings of the Second AAAI Conference on Human Computation and Crowdsourcing (HCOMP-14), pp.96--103, Pittsburgh, USA, 2014. acceptance rate = 26/80 = 32\%.
 \item Hiroshi Kajino, Yuta Tsuboi, Hisashi Kashima: Clustering Crowds, In Proceedings of the 27th AAAI Conference on Artificial Intelligence (AAAI-13), pp.1120-1127, Bellevue, Washington, USA, 2013. acceptance rate = 203/690 = 29\%.
 \item Hiroshi Kajino, Yuta Tsuboi, Issei Sato, Hisashi Kashima: Learning from Crowds and Experts, In Proceedings of the 4th Human Computation Workshop, pp.107-113, Toronto, Ontario, Canada, 2012.
 \item Hiroshi Kajino, Yuta Tsuboi, Hisashi Kashima: A Convex Formulation for Learning from Crowds, In Proceedings of the 26th AAAI Conference on Artificial Intelligence (AAAI-12), pp.73-79, Toronto, Ontario, Canada, 2012. acceptance rate = 294/1129 = 26\%.
\end{itemize}


\if0
\subsubsection*{Conference/Workshop Papers (non-refereed)}
\begin{itemize}
 \item Hiroshi Kajino: A Functional Dynamic Boltzmann Machine, The 31st Annual Conference of the Japanese Society for Artificial Intelligence, 2017. [in Japanese], JSAI Annual Conference Award.
 \item Hiroshi Kajino, Hiromi Arai, Jun Sakuma, Hisashi Kashima: Privacy-preserving Task Assignment in Crowdsourcing, The 29th Annual Conference of the Japanese Society for Artificial Intelligence, 2015. [in Japanese], JSAI Annual Conference Award.
 \item Hiroshi Kajino, Yukino Baba, Hisashi Kashima: Instance-privacy Preserving Crowdsourcing, The 28th Annual Conference of the Japanese Society for Artificial Intelligence, 2014. [in Japanese], JSAI Annual Conference Award.
 \item Hiroshi Kajino, Yuta Tsuboi, and Hisashi Kashima: Clustering Crowds, The 27th Annual Conference of the Japanese Society for Artificial Intelligence, 2013. [in Japanese]
 \item Hiroshi Kajino, Hiromi Arai, and Hisashi Kashima: Preserving Worker Privacy in Crowdsourcing Quality Control, In Proceedings of the 5th Forum on Data Engineering and Information Management, 2013. [in Japanese], DEIM2013 Presentation Award.
 \item Hiroshi Kajino, Yuta Tsuboi, Issei Sato, and Hisashi Kashima: Learning from Crowds and Experts, The 26th Annual Conference of the Japanese Society for Artificial Intelligence, 2012. [in Japanese]
 \item Hiroshi Kajino and Hisashi Kashima: A Convex Formulation of Learning from Crowds, In Proceedings of the 14th Information-Based Induction Science Workshop, pp.231-236, 2011. [in Japanese] Encouragement Award at IBIS 2011
\end{itemize}
\fi

\subsubsection*{Review Articles}
\begin{itemize}
 \item Hisashi Kashima, Hiroshi Kajino: Crowdsourcing and Machine Learning, Journal of the Japanese Society for Artificial Intelligence, Vol.27, No.4, pp.381-388, 2012. [in Japanese]
\end{itemize}


\subsection*{Awards}
\begin{itemize}
 \item 2018/07: JSAI Annual Conference Award
 \item 2017/07: JSAI Annual Conference Award
 \item 2015/07: JSAI Annual Conference Award
 \item 2014/07: JSAI Annual Conference Award
 \item 2013/06: JSAI Best Paper Award
 \item 2013/03: DEIM2013 Presentation Award
 \item 2011/11: Encouragement Award at IBIS 2011
\end{itemize}

\subsection*{Media coverage / press release}
\begin{itemize}
 \item 2021/09: The paper presented in ICML-21 was covered by Nikkei Robotics,  https://xtech.nikkei.com/atcl/nxt/mag/rob/18/012600001/00085/
 \item 2020/11: A chapter on AI application for digital transformation in a mook book published by the Nikkei Keizai Shinbun.
 \item 2018/03: A project on financial market forecasting with Mizuho bank, https://www.mizuhogroup.com/bank/news/2018/03/bank-ibm-new-ai-technology-for-financial-market-forecasting.html
\end{itemize}

\end{document}